Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-08 tex/sections/apm.tex
Fix minor readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Assume that we have a computing machine $M$, that accepts an input $in$ and produces an output $out$. We want to
calculate the output that results from applying $M$ on an initial input for $n$ times. Note that
$M$ may not be state-less:
\[
    M_n(in_1, out_1, out_2,\dots,out_{n-1}) \coloneqq out_n
\]

@@

Assume that we have a subcomponent that has a considerable arithmetic circuit complexity. Even if this subcomponent is
active in only a few computation steps, We will still have to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic hash calculator circuit during the
computation. At the end, to verify the functionality of the component, we use a final verification circuit.

@@

Now the prover needs to prove that he knows values $in_1,out_1,\dots,in_k,out_k$ such that they are correctly
produced by the component:
\[
    f((in_1,\dots,in_k)) = (out_1,\dots,out_k)
\]
and their digest is also correct:
\[
    h(in_1,out_1,\dots,in_k,out_k) = digest_f
\]
where functions $f$ and $h$, are both known to the prover and verifier.

>>>>

Assume that we have a computing machine $M$, that accepts an input $in$ and produces an output $out$. We want to
calculate the output that results from applying $M$ on an initial input for $n$ times. Note that
$M$ may or may not be state-less:
\[
    M_n(in_1, out_1, out_2,\dots,out_{n-1}) \coloneqq out_n
\]

@@

Assume that $M$ contains a subcomponent that has a considerable arithmetic circuit complexity.
Even if this subcomponent is
active in only a few computation steps, We will still have to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the subcomponent, we can use a simpler cryptographic hash calculator circuit during the
computation. At the end, we use a final verification circuit to verify the functionality of the component.

@@

Now the prover needs to prove that he knows values $in_1,out_1,in_2,out_2,\dots,in_k,out_k$ such that they are correctly
produced by the component:
\[
    f((in_1,\dots,in_k)) = (out_1,\dots,out_k)
\]
and their digest is also correct:
\[
    h(in_1,out_1,\dots,in_k,out_k) = digest_f
\]
where functions $f$ and $h$, are both known to the prover and verifier.
